\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\begin{document}

%%%%%%%%% TITLE
\title{Project Template for CSE 291-I00:Machine Learning for 3D Data}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}
\textbf{PLEASE READ}: \\
Kindly submit copies of your proposal by March 1. You can work in groups of two or three (not more than 3 please). Kindly use the CVPR template for your proposal. Make sure that your report is at least 3 pages (or more) including the references section. Also make sure to mention all the names of your collaborators in the report. Please submit one copy per group.
\section{Motivation}
Identify a problem to solve. In this section, describe the motivation behind trying to solve the particular problem, and how you think that your proposed solution is going to improve upon previous solutions. (25 marks)
\section{Background}
Describe adequate literature related to the task that you are studying. What are the current state-of-the-art methods currently employed to solve this problem? (25 marks)
\section{Method}
Describe the method that you are going to implement. Explain every component of the proposed model and also justify the reason for using the proposed method. (25 marks)
\section{Milestone}
Prepare a timeline and establish milestones. Divide your method into individual tasks and assign a particular time period to accomplish that task. This will help you in planning your project and completing it on time. (25 marks) 
{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}
